Sound Automated Synthesis of Digital Controllers

### 2016-10-13 paper/paper.tex
Noise formalisation

The ADC and DAC may be abstracted changing the hybrid system in figure~\ref{fig:sampledsystem} to the digital system in figure~\ref{fig:digsystem1} where the parametric uncertainties are represented by $\Delta G_{P}(z)=\mathcal{Z}\left\lbrace{G_{P}(s)}\right\rbrace$ and the entire effect of $\nu_{1}$ and $\nu_{2}$ in the output $Y(z)$ is represented as an additive (output) measurement noise $\nu(z)$.

@@

Finally, the quantisation noise may be considered a energy-bounded signal (Lemma~\ref{lemma:boundednoise}) and thus $\hat{Y}(z)$ will be bounded and the closed-loop system stable if the conditions in Lemma~\ref{lemma:eq_int_stab} are followed.

>>>>

The ADC and DAC may be abstracted changing the hybrid system in figure~\ref{fig:sampledsystem} to the digital system in figure~\ref{fig:digsystem1} where the parametric uncertainties are represented by $\Delta G_{P}(z)=\mathcal{Z}\left\lbrace{G_{P}(s)}\right\rbrace$ and the entire effect of $\nu_{1}$ and $\nu_{2}$ in the output $Y(z)$ is represented as an additive (output) measurement noise $\nu(z)$, thus $\hat{Y}(z)=Y(z)+\nu(z)$. The measurement noise $\nu(k)$ is enough for represent both quantization noises ($\nu_{1}$ and $\nu_{2}$) what can be obtained reorganizing the equations~\ref{eq:outputfunctions}:
\begin{equation}
\label{eq:outputfunctions2}
\hat{Y}(z)=H_{1}R(z)+H_{1}\nu_{1}(z)+H_{2}(z)\nu_{2}(z),
\end{equation}
where $H_{1}R(z)$ is exactly equal to $Y(z)$ without quantization noise effects, thus:
\begin{equation}
\nu(z)=H_{1}\nu_{1}(z)+H_{2}(z)\nu_{2}(z).
\end{equation}

%The system in equation~\ref{controller_plant_tf} (disregarding the $\Delta{G}_{P}(z)$ may be represented by the following difference equation model:
%\begin{equation}
%\begin{split}
%y(k)=-a_{1}y(k-1)-a_{2}y(k-2)-\cdots - a_{N}y(k-N)\\
%+b_{0}u(k)+b_{1}u(k-1)+b_{2}u(k-2)+\cdots+b_{M}u(k-M),
%\end{split}
%\end{equation}
%and consequently $\hat{y}(k)$ may be represented by the following difference equation:
%\begin{equation}
%\label{eq:differencewithnoise}
%\begin{split}
%\hat{y}(k)=-a_{1}y(k-1)-a_{2}y(k-2)-\cdots - a_{N_{G}}y(k-N_{G})\\
%+b_{0}u(k)+b_{1}u(k-1)+b_{2}u(k-2)+\cdots+b_{M_{G}}u(k-M_{G})+\nu(k).
%\end{split}
%\end{equation}
%
%The z-transform of~\eqref{eq:differencewithnoise} is:
%\begin{equation}
%\begin{split}
%\hat{Y}(z)=(-a_{1}z^{-1}-a_{2}z^{-2}-\cdots-a_{N_{G}}z^{-N_{G}})Y(z)\\
%+(b_{0}+b_{1}z^{-1}+b_{2}z^{-2}+\cdots+b_{M_{G}}z^{-M_{G}})U(z)+\nu(z),
%\end{split}
%\end{equation}
%dividing both sides by $U(z)$, it is equivalent to:
%\begin{equation}
%\frac{\hat{Y}(z)}{U(z)}=[1-D_{G}(z)]G(z)+U(z)D_{G}(z)+\frac{\nu(z)}{U(z)}=G(z)+\Delta{G}_{Q}(z),
%\end{equation}

%Considering the quantization noise $\nu(k)$ as an output error in discrete plant model, we may represent it as an additive noise in the plant output $y(k)$ resulting in the noisy output $\hat{y}(k)$:
%\begin{equation}
%
%\end{equation}

This noise $\nu(z)$ may represent exactly the same effects that $\nu_{1}(z)$ and $\nu_{2}(z)$ represents together.

@@

Finally, the quantisation noise spectrum may be considered a energy-bounded (Lemma~\ref{lemma:boundednoise}), and consequently the Parseval's theorem ensures that the quantisation noise is also energy-bounded in time-domain.  Thus $\hat{Y}(z)$ will be bounded and the closed-loop system stable if the conditions in Lemma~\ref{lemma:eq_int_stab} are followed.
